N-Body problem

### 2014-10-25 article/article.tex
Adds graph and sections results

@@

results

>>>>

\label{verification}

@@

The results of each model implementation are compared using the metrics designed in section~\ref{verification}. Using these methods allows us to compare the performance of each model. For all the energy comparison methods we used a fixed total \textit{model evaluation time}, i.e. we simulate 100 model minutes. Depending on the time-steps used in each method, this might take more or less iterations to calculate, meaning that the total simulation time increases. In
section~\ref{sec:res:euler} compares the relative error of the Euler method using different time-steps. Also, section~\ref{sec:res:taylor} compares the improvement of adding an extra term in the Taylor expansion. And, section~\ref{sec:res:leapfrog} shows the results using the Leapfrog integrator and all the models are compared in the last section~\ref{sec:res:all}.

\subsection{Euler}
\label{sec:res:euler}
To verify our model, we have defined the energy metrics. In this experiment the relative energy metric as defined in section~\ref{XXX} is used. In total we have compared four different time-steps to evaluate the performance effect of an increasing/decreasing time-step. The time-steps used are $0.001, 0.01, 0.1, 1$ and figure~\ref{fig:euler} shows a plot of the relative energy error for the \textit{model simulation time}. 
\begin{figure}
\label{fig:euler}
    \includegraphics[width=0.9\textwidth]{euler_different_timesteps.png}
    \caption{Relative energy error for the Euler integrator using different time-steps for a fixed total model simulation time.}
\end{figure}

\subsection{Taylor}
\label{sec:res:taylor}

\subsection{Leapfrog}
\label{sec:res:leapfrog}

\subsection{All models}
\label{sec:res:all}
